Computing Entropies with Nested Sampling

### 2017-10-16 talk/ms.tex
Hard integrals slide
Pasted a slide from NS talk

>>>>

% New slide
\begin{frame}
\frametitle{Hard integrals}

E.g.
\begin{align}
H(\theta|d) &= -\int p(d) \int p(\theta|d) \log p(\theta|d) \, d\theta \, dd \\
            &= -\int p(d) \int p(\theta|d)
                    \log\left[\frac{p(\theta)p(d|\theta)}{p(d)}\right] \, d\theta \, dd
\end{align}

But $p(d)$, sitting there inside a logarithm, is already supposed to be
a hard integral (the marginal likelihood / evidence)...

\begin{align}
p(d) &= \int p(\theta) p(d|\theta) \, d\theta
\end{align}

% New slide
\begin{frame}
\frametitle{Nested Sampling uses {\em constrained priors}}
Instead of using a sequence of distributions
defined by $\pi(\theta)L(\theta)^{1/T}$, use a sequence defined by

\begin{align*}
p(\theta; \ell) &\propto \left\{
    \begin{array}{lr}
        \pi(\theta), & L(\theta) > \ell\\
        0,           & \textnormal{otherwise}.
    \end{array}
\right.
\end{align*}
and have $\ell$ increase at a controlled rate, so that enclosed prior mass
shrinks {\em geometrically}.
